Reproducible and programmatic generation of neuroimaging visualizations

### 2022-04-25 manuscript.Rmd
fig fix

---
title: Reproducible and programmatic generation of neuroimaging visualizations
authors:
  - name: Sidhant Chopra
    thanks: Corresponding author
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
    email: sidhant.chopra@yale.com
  - name: Loïc Labache
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Edwina R Orchard
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Avram Holmes
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
keywords:
  - Neuroimaging visualization
  - Reproducibility 
  - Programmatic figures
  - Open Science
  - R
output: 
  bookdown::word_document2:
    toc: false
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    keep_tex: true
    latex_engine: lualatex
linestretch: 2
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}\doublespacing
---

@@

Precise controls via code over visualization settings, such as color schemes, legend placement and camera angles, can provide you with much greater flexibility over visualizations. Nonetheless, part of the appeal of GUI-based tools is that the presets for such settings can provide a useful starting point and reduce the decision burden on novice users. However, similar presets are often available in the form of default settings across most code-based packages, negating the need for the user to manually enter each and every choice of setting required for creating an image. Most code-based tools also come with documentation, with R-packages on the *CRAN* or *Neuroconductor* (Muschelli et al., 2019) repositories having compulsory requirements for detailed guidance. Recent packages have even started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, & Mejia, 2022; Mowinckel & Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer & Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users. As the popularity of code-sharing for figure increases, there will be a cornucopia of templates that can be used as the basis for new figures.

@@

Increasingly popular software such as *R Markdown*, *Quarto* and *Jupyter Notebook* allow for the mixing of prose and code in a single script, resulting in fully reproducible and publication ready papers. By using code-based tools available within your preferred environment, brain visualizations can be directly integrated and embedded within a paper or report. For instance, a fully reproducible version of the current paper can be found on [GitHub](https://github.com/sidchop/Brain_comms_field_potential). Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g. *e-Life*, *Aperture Neuro*), with other journals like *F1000Research* and *GigaScience* even allowing on-demand re-running of code computational environment linked to the associated article using 'compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021),

@@

Often cerebellar and brain-stem regions are not well represented in software (e.g. Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, & Holmes). Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based visualization tools.

As can be seen in Table 1, there are usually multiple packages within each programming environment which are capable of visualizing each data time. While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools. Future work should continue to consolidate brain visualization methods into unified beginner-friendly tools which are capable of plotting multiple data types.

@@

patchwork <- figs[[1]]/figs[[2]]|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]]|(figs[[3]]/figs[[4]]/figs[[10]])

@@

library(neurobase)
library(ggplotify)

@@

#Use the ortho2 function from the neurobase package to make the figure
ortho2(x = template,   #Specify the background template
       y = effect,     #Specify the effect you want to overlay on the tempplate
       crosshairs = F, #Remove the cross-hairs
       bg = "white",   #Make the background white 
       NA.x = T,       #Do not display NA values
       col.y= viridis::viridis(n = 500), #Select the color scale. In this case I have used the viridis scale from the viridis package. 
       xyz = c(70,50,80), #set the x y & z slice you want to visualise
       useRaster = T,     #Sometimes using Raster makes for clearer plots
       ycolorbar = TRUE,  #Add a color bar
       mfrow = c(1,1)) + 
  colorbar(breaks,col = viridis::viridis(n=length(breaks)-1), 
           text.col = "black", labels = TRUE, maxleft = 0.95)  #Set the specifications for the colorbar

@@

png('data/fig1b.png')
overlay(x=robust_window(t1), y=atlas, 
        plot.type = "single", 
        z=c(seq(30,110,10)), 
        col.y =  alpha(rainbow(300), 0.3),
        plane = "axial",  
        useRaster = T, 
        bg = "white",
        NA.x=T, 
        zlim.y =c(1,300))

@@

view_xifti_surface(cii, 
                   hemisphere = "both", 
                   view = "lateral", 
                   idx = 1,
                   colors = viridis::viridis(n = 100),
                   zlim = c(1.2,1.5),  
                   legend_embed = T,
                   cex.title = 2)

@@

colourmap <- colorRampPalette(viridis::viridis(n = 1000))
fsbrain.set.default.figsize(700, 700);

@@

#remotes::install_github("sidchop/brainconn")
library(brainconn)

conmat <- example_weighted_undirected
degree <- rowSums(conmat)[which(rowSums(conmat)!=0)]
fig1h <- brainconn(atlas ="schaefer300_n7", 
                   conmat=conmat, 
                   node.size = degree/2,
                   view="ortho", 
                   edge.color.weighted = T,
                   background.alpha = 0.4, 
                   show.legend = F,
                   edge.color = scale_edge_colour_gradient2(low='yellow', mid='orange', high='red')) 
ggsave(filename = 'data/fig1h.png', 
       plot = fig1h, 
       device = 'png',
       bg = 'white',
       height = 7, 
       units = "in")

>>>>

---
title: Reproducible and programmatic generation of neuroimaging visualizations
authors:
  - name: Sidhant Chopra
    thanks: Corresponding author
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
    email: sidhant.chopra@yale.com
  - name: Loïc Labache
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Edwina R Orchard
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Avram Holmes
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
keywords:
  - Neuroimaging visualization
  - Reproducibility 
  - Programmatic figures
  - Open Science
  - R
output: 
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    keep_tex: true
    latex_engine: lualatex
  bookdown::word_document2:
    toc: false
linestretch: 2
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}\doublespacing
---

@@

Precise controls via code over visualization settings, such as color schemes, legend placement and camera angles, can provide you with much greater flexibility over visualizations. Nonetheless, part of the appeal of GUI-based tools is that the presets for such settings can provide a useful starting point and reduce the decision burden on novice users. However, similar presets are often available in the form of default settings across most code-based packages, negating the need for the user to manually enter each and every choice of setting required for creating an image. Most code-based tools also come with documentation, with R-packages on the *CRAN* or *Neuroconductor* (Muschelli et al., 2019) repositories having compulsory requirements for detailed guidance. Recent packages have started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, & Mejia, 2022; Mowinckel & Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer & Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users. As the popularity of code-sharing for figure increases, there will be a cornucopia of templates that can be used as the basis for new figures.

@@

Increasingly popular software such as *R Markdown*, *Quarto* and *Jupyter Notebook* allow for the mixing of prose and code in a single script, resulting in fully reproducible and publication ready papers. By using code-based tools available within your preferred environment, brain visualizations can be directly integrated and embedded within a paper or report. For instance, a fully reproducible version of the current paper can be found on [GitHub](https://github.com/sidchop/Brain_comms_field_potential). Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g. *e-Life*, *Aperture Neuro*), with other journals like *F1000Research* and *GigaScience* even allowing on-demand re-running of code computational environment linked to the associated article using 'compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021).

@@

Often cerebellar and brain-stem regions are not well represented in software (e.g. Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, & Holmes, 2022). Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based visualization tools.

As can be seen in Table 1, there are usually multiple packages within each programming environment which are capable of visualizing each data time. While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools. Future work should continue to consolidate brain visualization methods into unified beginner-friendly code-based tools which are capable of plotting multiple data types.

@@

patchwork <- figs[[1]]/figs[[2]]|((figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]])+plot_layout(heights = c(0.8,0.8,1.5))|((figs[[3]]/figs[[4]]/figs[[10]])+plot_layout(heights = c(0.7,1,1)))
patchwork + plot_annotation(tag_levels = 'A',
                            title = 'Examples of brain visualizations in R') &
    theme(plot.tag = element_text(face = 'bold'),
          plot.title = element_text(face="bold"))

@@

library(neurobase)

@@

#Use the ortho2 function from the neurobase package to make the figure
ortho2(x = template,   #Specify the background template
       y = effect,     #Specify the effect you want to overlay on the tempplate
       crosshairs = F, #Remove the cross-hairs
       bg = "white",   #Make the background white 
       NA.x = T,       #Do not display NA values
       col.y= rev(viridis::inferno(n = 500)), #Select the color scale. In this case I have used the viridis scale from the viridis package. 
       xyz = c(70,50,80), #set the x y & z slice you want to visualise
       useRaster = T,     #Sometimes using Raster makes for clearer plots
       ycolorbar = TRUE,  #Add a color bar
       mfrow = c(1,1)) + 
  colorbar(breaks, col = rev(viridis::inferno(n=length(breaks)-1)), 
           text.col = "black", labels = TRUE, maxleft = 0.95)  #Set the specifications for the colorbar

@@

png('data/fig1b.png')
overlay(x=robust_window(t1), y=atlas, 
        plot.type = "single", 
        z=c(seq(30,110,10)), 
        col.y =  alpha(viridis::inferno(300), 0.6),
        plane = "axial",  
        useRaster = T, 
        bg = "white",
        NA.x=T, 
        zlim.y =c(1,300))

@@

view_xifti_surface(cii, 
                   hemisphere = "both", 
                   view = "lateral", 
                   idx = 1,
                   colors = viridis::plasma(n = 100),
                   zlim = c(1.2,1.5),  
                   legend_embed = T,
                   cex.title = 2)

@@

colourmap <- colorRampPalette(viridis::plasma(n = 1000))
fsbrain.set.default.figsize(700, 700);

@@

#devtools::install_github("sidchop/brainconn")
library(brainconn)

conmat <- example_weighted_undirected
degree <- rowSums(conmat)[which(rowSums(conmat)!=0)]

brainconn(atlas ="schaefer300_n7", 
                   conmat=conmat, 
                   node.size = degree/2,
                   view="top", 
                   edge.color.weighted = T,
                   background.alpha = 0.8, 
                   show.legend = F, 
                   edge.color = scale_edge_colour_viridis())

ggsave(filename = 'data/fig1h.png', 
       plot = fig1h, 
       device = 'png',
       bg = 'white',
       height = 7, 
       units = "in")

### 2022-04-25 manuscript.tex
fig fix

Precise controls via code over visualization settings, such as color schemes, legend placement and camera angles, can provide you with much greater flexibility over visualizations. Nonetheless, part of the appeal of GUI-based tools is that the presets for such settings can provide a useful starting point and reduce the decision burden on novice users. However, similar presets are often available in the form of default settings across most code-based packages, negating the need for the user to manually enter each and every choice of setting required for creating an image. Most code-based tools also come with documentation, with R-packages on the \emph{CRAN} or \emph{Neuroconductor} (Muschelli et al., 2019) repositories having compulsory requirements for detailed guidance. Recent packages have even started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, \& Mejia, 2022; Mowinckel \& Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer \& Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users. As the popularity of code-sharing for figure increases, there will be a cornucopia of templates that can be used as the basis for new figures.

@@

Increasingly popular software such as \emph{R Markdown}, \emph{Quarto} and \emph{Jupyter Notebook} allow for the mixing of prose and code in a single script, resulting in fully reproducible and publication ready papers. By using code-based tools available within your preferred environment, brain visualizations can be directly integrated and embedded within a paper or report. For instance, a fully reproducible version of the current paper can be found on \href{https://github.com/sidchop/Brain_comms_field_potential}{GitHub}. Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g.~\emph{e-Life}, \emph{Aperture Neuro}), with other journals like \emph{F1000Research} and \emph{GigaScience} even allowing on-demand re-running of code computational environment linked to the associated article using `compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021),

@@

Often cerebellar and brain-stem regions are not well represented in software (e.g.~Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, \& Holmes). Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based visualization tools.

As can be seen in Table 1, there are usually multiple packages within each programming environment which are capable of visualizing each data time. While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools. Future work should continue to consolidate brain visualization methods into unified beginner-friendly tools which are capable of plotting multiple data types.

@@

\FunctionTok{library}\NormalTok{(neurobase)}
\FunctionTok{library}\NormalTok{(ggplotify)}

@@

\CommentTok{\#Use the ortho2 function from the neurobase package to make the figure}
\FunctionTok{ortho2}\NormalTok{(}\AttributeTok{x =}\NormalTok{ template,   }\CommentTok{\#Specify the background template}
       \AttributeTok{y =}\NormalTok{ effect,     }\CommentTok{\#Specify the effect you want to overlay on the tempplate}
       \AttributeTok{crosshairs =}\NormalTok{ F, }\CommentTok{\#Remove the cross{-}hairs}
       \AttributeTok{bg =} \StringTok{"white"}\NormalTok{,   }\CommentTok{\#Make the background white }
       \AttributeTok{NA.x =}\NormalTok{ T,       }\CommentTok{\#Do not display NA values}
       \AttributeTok{col.y=}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{), }\CommentTok{\#Select the color scale. In this case I have used the viridis scale from the viridis package. }
       \AttributeTok{xyz =} \FunctionTok{c}\NormalTok{(}\DecValTok{70}\NormalTok{,}\DecValTok{50}\NormalTok{,}\DecValTok{80}\NormalTok{), }\CommentTok{\#set the x y \& z slice you want to visualise}
       \AttributeTok{useRaster =}\NormalTok{ T,     }\CommentTok{\#Sometimes using Raster makes for clearer plots}
       \AttributeTok{ycolorbar =} \ConstantTok{TRUE}\NormalTok{,  }\CommentTok{\#Add a color bar}
       \AttributeTok{mfrow =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} 
  \FunctionTok{colorbar}\NormalTok{(breaks,}\AttributeTok{col =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n=}\FunctionTok{length}\NormalTok{(breaks)}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{), }
           \AttributeTok{text.col =} \StringTok{"black"}\NormalTok{, }\AttributeTok{labels =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{maxleft =} \FloatTok{0.95}\NormalTok{)  }\CommentTok{\#Set the specifications for the colorbar}

@@

\FunctionTok{png}\NormalTok{(}\StringTok{\textquotesingle{}data/fig1b.png\textquotesingle{}}\NormalTok{)}
\FunctionTok{overlay}\NormalTok{(}\AttributeTok{x=}\FunctionTok{robust\_window}\NormalTok{(t1), }\AttributeTok{y=}\NormalTok{atlas, }
        \AttributeTok{plot.type =} \StringTok{"single"}\NormalTok{, }
        \AttributeTok{z=}\FunctionTok{c}\NormalTok{(}\FunctionTok{seq}\NormalTok{(}\DecValTok{30}\NormalTok{,}\DecValTok{110}\NormalTok{,}\DecValTok{10}\NormalTok{)), }
        \AttributeTok{col.y =}  \FunctionTok{alpha}\NormalTok{(}\FunctionTok{rainbow}\NormalTok{(}\DecValTok{300}\NormalTok{), }\FloatTok{0.3}\NormalTok{),}
        \AttributeTok{plane =} \StringTok{"axial"}\NormalTok{,  }
        \AttributeTok{useRaster =}\NormalTok{ T, }
        \AttributeTok{bg =} \StringTok{"white"}\NormalTok{,}
        \AttributeTok{NA.x=}\NormalTok{T, }
        \AttributeTok{zlim.y =}\FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{300}\NormalTok{))}

@@

\FunctionTok{view\_xifti\_surface}\NormalTok{(cii, }
                   \AttributeTok{hemisphere =} \StringTok{"both"}\NormalTok{, }
                   \AttributeTok{view =} \StringTok{"lateral"}\NormalTok{, }
                   \AttributeTok{idx =} \DecValTok{1}\NormalTok{,}
                   \AttributeTok{colors =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{100}\NormalTok{),}
                   \AttributeTok{zlim =} \FunctionTok{c}\NormalTok{(}\FloatTok{1.2}\NormalTok{,}\FloatTok{1.5}\NormalTok{),  }
                   \AttributeTok{legend\_embed =}\NormalTok{ T,}
                   \AttributeTok{cex.title =} \DecValTok{2}\NormalTok{)}

@@

\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{))}
\FunctionTok{fsbrain.set.default.figsize}\NormalTok{(}\DecValTok{700}\NormalTok{, }\DecValTok{700}\NormalTok{);}

@@

\CommentTok{\#remotes::install\_github("sidchop/brainconn")}
\FunctionTok{library}\NormalTok{(brainconn)}

\NormalTok{conmat }\OtherTok{\textless{}{-}}\NormalTok{ example\_weighted\_undirected}
\NormalTok{degree }\OtherTok{\textless{}{-}} \FunctionTok{rowSums}\NormalTok{(conmat)[}\FunctionTok{which}\NormalTok{(}\FunctionTok{rowSums}\NormalTok{(conmat)}\SpecialCharTok{!=}\DecValTok{0}\NormalTok{)]}
\NormalTok{fig1h }\OtherTok{\textless{}{-}} \FunctionTok{brainconn}\NormalTok{(}\AttributeTok{atlas =}\StringTok{"schaefer300\_n7"}\NormalTok{, }
                   \AttributeTok{conmat=}\NormalTok{conmat, }
                   \AttributeTok{node.size =}\NormalTok{ degree}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
                   \AttributeTok{view=}\StringTok{"ortho"}\NormalTok{, }
                   \AttributeTok{edge.color.weighted =}\NormalTok{ T,}
                   \AttributeTok{background.alpha =} \FloatTok{0.4}\NormalTok{, }
                   \AttributeTok{show.legend =}\NormalTok{ F,}
                   \AttributeTok{edge.color =} \FunctionTok{scale\_edge\_colour\_gradient2}\NormalTok{(}\AttributeTok{low=}\StringTok{\textquotesingle{}yellow\textquotesingle{}}\NormalTok{, }\AttributeTok{mid=}\StringTok{\textquotesingle{}orange\textquotesingle{}}\NormalTok{, }\AttributeTok{high=}\StringTok{\textquotesingle{}red\textquotesingle{}}\NormalTok{)) }
\FunctionTok{ggsave}\NormalTok{(}\AttributeTok{filename =} \StringTok{\textquotesingle{}data/fig1h.png\textquotesingle{}}\NormalTok{, }
       \AttributeTok{plot =}\NormalTok{ fig1h, }
       \AttributeTok{device =} \StringTok{\textquotesingle{}png\textquotesingle{}}\NormalTok{,}
       \AttributeTok{bg =} \StringTok{\textquotesingle{}white\textquotesingle{}}\NormalTok{,}
       \AttributeTok{height =} \DecValTok{7}\NormalTok{, }
       \AttributeTok{units =} \StringTok{"in"}\NormalTok{)}

>>>>

Precise controls via code over visualization settings, such as color schemes, legend placement and camera angles, can provide you with much greater flexibility over visualizations. Nonetheless, part of the appeal of GUI-based tools is that the presets for such settings can provide a useful starting point and reduce the decision burden on novice users. However, similar presets are often available in the form of default settings across most code-based packages, negating the need for the user to manually enter each and every choice of setting required for creating an image. Most code-based tools also come with documentation, with R-packages on the \emph{CRAN} or \emph{Neuroconductor} (Muschelli et al., 2019) repositories having compulsory requirements for detailed guidance. Recent packages have started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, \& Mejia, 2022; Mowinckel \& Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer \& Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users. As the popularity of code-sharing for figure increases, there will be a cornucopia of templates that can be used as the basis for new figures.

@@

Increasingly popular software such as \emph{R Markdown}, \emph{Quarto} and \emph{Jupyter Notebook} allow for the mixing of prose and code in a single script, resulting in fully reproducible and publication ready papers. By using code-based tools available within your preferred environment, brain visualizations can be directly integrated and embedded within a paper or report. For instance, a fully reproducible version of the current paper can be found on \href{https://github.com/sidchop/Brain_comms_field_potential}{GitHub}. Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g.~\emph{e-Life}, \emph{Aperture Neuro}), with other journals like \emph{F1000Research} and \emph{GigaScience} even allowing on-demand re-running of code computational environment linked to the associated article using `compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021).

@@

Often cerebellar and brain-stem regions are not well represented in software (e.g.~Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, \& Holmes, 2022). Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based visualization tools.

As can be seen in Table 1, there are usually multiple packages within each programming environment which are capable of visualizing each data time. While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools. Future work should continue to consolidate brain visualization methods into unified beginner-friendly code-based tools which are capable of plotting multiple data types.

@@

\FunctionTok{library}\NormalTok{(neurobase)}

@@

\CommentTok{\#Use the ortho2 function from the neurobase package to make the figure}
\FunctionTok{ortho2}\NormalTok{(}\AttributeTok{x =}\NormalTok{ template,   }\CommentTok{\#Specify the background template}
       \AttributeTok{y =}\NormalTok{ effect,     }\CommentTok{\#Specify the effect you want to overlay on the tempplate}
       \AttributeTok{crosshairs =}\NormalTok{ F, }\CommentTok{\#Remove the cross{-}hairs}
       \AttributeTok{bg =} \StringTok{"white"}\NormalTok{,   }\CommentTok{\#Make the background white }
       \AttributeTok{NA.x =}\NormalTok{ T,       }\CommentTok{\#Do not display NA values}
       \AttributeTok{col.y=} \FunctionTok{rev}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{inferno}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{)), }\CommentTok{\#Select the color scale. In this case I have used the viridis scale from the viridis package. }
       \AttributeTok{xyz =} \FunctionTok{c}\NormalTok{(}\DecValTok{70}\NormalTok{,}\DecValTok{50}\NormalTok{,}\DecValTok{80}\NormalTok{), }\CommentTok{\#set the x y \& z slice you want to visualise}
       \AttributeTok{useRaster =}\NormalTok{ T,     }\CommentTok{\#Sometimes using Raster makes for clearer plots}
       \AttributeTok{ycolorbar =} \ConstantTok{TRUE}\NormalTok{,  }\CommentTok{\#Add a color bar}
       \AttributeTok{mfrow =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} 
  \FunctionTok{colorbar}\NormalTok{(breaks, }\AttributeTok{col =} \FunctionTok{rev}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{inferno}\NormalTok{(}\AttributeTok{n=}\FunctionTok{length}\NormalTok{(breaks)}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{)), }
           \AttributeTok{text.col =} \StringTok{"black"}\NormalTok{, }\AttributeTok{labels =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{maxleft =} \FloatTok{0.95}\NormalTok{)  }\CommentTok{\#Set the specifications for the colorbar}

@@

\FunctionTok{png}\NormalTok{(}\StringTok{\textquotesingle{}data/fig1b.png\textquotesingle{}}\NormalTok{)}
\FunctionTok{overlay}\NormalTok{(}\AttributeTok{x=}\FunctionTok{robust\_window}\NormalTok{(t1), }\AttributeTok{y=}\NormalTok{atlas, }
        \AttributeTok{plot.type =} \StringTok{"single"}\NormalTok{, }
        \AttributeTok{z=}\FunctionTok{c}\NormalTok{(}\FunctionTok{seq}\NormalTok{(}\DecValTok{30}\NormalTok{,}\DecValTok{110}\NormalTok{,}\DecValTok{10}\NormalTok{)), }
        \AttributeTok{col.y =}  \FunctionTok{alpha}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{inferno}\NormalTok{(}\DecValTok{300}\NormalTok{), }\FloatTok{0.6}\NormalTok{),}
        \AttributeTok{plane =} \StringTok{"axial"}\NormalTok{,  }
        \AttributeTok{useRaster =}\NormalTok{ T, }
        \AttributeTok{bg =} \StringTok{"white"}\NormalTok{,}
        \AttributeTok{NA.x=}\NormalTok{T, }
        \AttributeTok{zlim.y =}\FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{300}\NormalTok{))}

@@

\FunctionTok{view\_xifti\_surface}\NormalTok{(cii, }
                   \AttributeTok{hemisphere =} \StringTok{"both"}\NormalTok{, }
                   \AttributeTok{view =} \StringTok{"lateral"}\NormalTok{, }
                   \AttributeTok{idx =} \DecValTok{1}\NormalTok{,}
                   \AttributeTok{colors =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{plasma}\NormalTok{(}\AttributeTok{n =} \DecValTok{100}\NormalTok{),}
                   \AttributeTok{zlim =} \FunctionTok{c}\NormalTok{(}\FloatTok{1.2}\NormalTok{,}\FloatTok{1.5}\NormalTok{),  }
                   \AttributeTok{legend\_embed =}\NormalTok{ T,}
                   \AttributeTok{cex.title =} \DecValTok{2}\NormalTok{)}

@@

\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{plasma}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{))}
\FunctionTok{fsbrain.set.default.figsize}\NormalTok{(}\DecValTok{700}\NormalTok{, }\DecValTok{700}\NormalTok{);}

@@

\CommentTok{\#devtools::install\_github("sidchop/brainconn")}
\FunctionTok{library}\NormalTok{(brainconn)}

\NormalTok{conmat }\OtherTok{\textless{}{-}}\NormalTok{ example\_weighted\_undirected}
\NormalTok{degree }\OtherTok{\textless{}{-}} \FunctionTok{rowSums}\NormalTok{(conmat)[}\FunctionTok{which}\NormalTok{(}\FunctionTok{rowSums}\NormalTok{(conmat)}\SpecialCharTok{!=}\DecValTok{0}\NormalTok{)]}

\FunctionTok{brainconn}\NormalTok{(}\AttributeTok{atlas =}\StringTok{"schaefer300\_n7"}\NormalTok{, }
                   \AttributeTok{conmat=}\NormalTok{conmat, }
                   \AttributeTok{node.size =}\NormalTok{ degree}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
                   \AttributeTok{view=}\StringTok{"top"}\NormalTok{, }
                   \AttributeTok{edge.color.weighted =}\NormalTok{ T,}
                   \AttributeTok{background.alpha =} \FloatTok{0.8}\NormalTok{, }
                   \AttributeTok{show.legend =}\NormalTok{ F, }
                   \AttributeTok{edge.color =} \FunctionTok{scale\_edge\_colour\_viridis}\NormalTok{()) }

\FunctionTok{ggsave}\NormalTok{(}\AttributeTok{filename =} \StringTok{\textquotesingle{}data/fig1h.png\textquotesingle{}}\NormalTok{, }
       \AttributeTok{plot =}\NormalTok{ fig1h, }
       \AttributeTok{device =} \StringTok{\textquotesingle{}png\textquotesingle{}}\NormalTok{,}
       \AttributeTok{bg =} \StringTok{\textquotesingle{}white\textquotesingle{}}\NormalTok{,}
       \AttributeTok{height =} \DecValTok{7}\NormalTok{, }
       \AttributeTok{units =} \StringTok{"in"}\NormalTok{)}
